\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

\wss{What will you be demonstrating}

For the Proof-of-Concept (POC) demonstration, our team will present a high-level prototype of the instructor dashboard using simulated gaze data. The goal of the demo is to illustrate the envisioned system workflow and demonstrate progress toward the project’s main objectives of data visualization and real-time analytics.

The demonstration will feature a preliminary dashboard interface that displays group gaze information and analytics for classroom activities. Mock data will be used to emulate gaze streams from multiple eye-tracking devices, showcasing how the system could process and visualize engagement patterns.

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Angela Zeng & 9\\
Ann Shi & 8\\
Ibrahim Sahi & 9\\
Manan Sharma & 9\\
Stanley Chen & 8\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\noindent \textbf{Supervisor's Name: } Dr. Irene Yuan, Dr. Lauren Fink

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Angela Zeng & 4\\
Ann Shi & 5\\
Ibrahim Sahi & 4\\
Manan Sharma & 4\\
Stanley Chen & 4\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13\\
Angela Zeng & 7\\
Ann Shi & 6\\
Ibrahim Sahi & 6\\
Manan Sharma & 5\\
Stanley Chen & 6\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [Lucas Dutton]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Angela Zeng & 3\\
Ann Shi & 2\\
Manan Sharma & 3\\
Ibrahim Sahi & 2\\
Stanley Chen & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 72 & 100\% \\
Angela Zeng & 18 & 25\% \\
Ann Shi & 17 & 24\% \\
Manan Sharma & 18 & 25\% \\
Ibrahim Sahi & 12 & 17\% \\
Stanley Chen & 7 & 10\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Angela Zeng & 12 & 11 \\
Ann Shi & 17 & 15 \\
Ibrahim Sahi & 2 & 1 \\
Manan Sharma & 5 & 4 \\
Stanley Chen & 2 & 2 \\
\bottomrule
\end{tabular}
\end{table}

Note: Size of issues vary which explains why some members have more issues than others. 

\section{CICD}
We will run GitHub Actions on every PR. The jobs will include \texttt{lint}, \texttt{test}, and \texttt{build} all to ensure code quality. A PR will not merge unless all jobs succeed. Secrets and environment variables will be stored in GitHub Actions Secrets to keep them secure. Environments will require approval for deploy jobs if added later.

\section{Team Charter Trigger Items}

Our team’s main triggers are based on punctuality, attendance, and accountability. We agreed on a 10-minute grace period for lateness, weekly meetings (Thursday tutorial and Saturday follow-up), and equal contribution to all assigned tasks. Respectful communication and preparedness for meetings were also identified as key behavioral expectations. \\

So far, the team has largely met the agreed-upon standards. Minor lateness occurred in a few cases but always within the grace period or with prior notice. And when members of team were going to be quite late, they would always inform us ahead of time. There were no significant violations related to contribution quality, respect, or teamwork. \\

If punctuality or contribution issues become recurring, we will first discuss them as a group during the next meeting. Repeated issues would lead to redistributing workload temporarily and, if necessary, consulting the TA for mediation. We will also review whether any triggers (e.g., the grace period or workload expectations) should be adjusted to better match team circumstances

\section{Additional Productivity Metrics}

N/A

\end{document}