\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Productivity: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments.tex}
\input{../Common.tex}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the PoC demo and the Rev
0 demo; the contributions prior to the PoC are NOT included.

\wss{Please do not delete sections or modify the table formats.  Standardization
helps the instructors and TAs to review these documents. You may add sections to
the report.}

\wss{Remove the instructor guidelines/comments in the final version.}

\wss{Fill in the requested information, like project url, TA name, supervisor name, etc.}

\section{Demo Plans}

\wss{What will you be demonstrating}

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Angela Zeng & 4\\
Ann Shi & 4\\
Manan Sharma & 4\\
Ibrahim Sahi & 4\\
Stanley Chen & 4\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\noindent \textbf{Supervisor's Name: Lauren Fink} 

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & Num\\
Angela Zeng & Num\\
Ann Shi & Num\\
Manan Sharma & Num\\
Ibrahim Sahi & Num\\
Stanley Chen & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo. You can find the number of lectures in the time period of
interest by looking at the
\href{https://calendar.google.com/calendar/u/0/embed?src=rnboqiaki1k2la7rpu3bn0um58@group.calendar.google.com&ctz=America/Toronto}
{Google calendar} for the capstone course. The first entry in the
table should be the total number of lectures held for the class during the period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & Num\\
Angela Zeng & 1\\
Ann Shi & 0\\
Manan Sharma & 1\\
Ibrahim Sahi & 0\\
Stanley Chen & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: Lucas}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & Num\\
Angela Zeng & 0\\
Ann Shi & 0\\
Manan Sharma & 0\\
Ibrahim Sahi & 0\\
Stanley Chen & 0\\
\bottomrule
\end{tabular}
\end{table}

\wss{We were all unable to attend any TA document discussion meetings due to the snow day on January 15th. We as a team decided a meeting with the TA was not necessary as we simply asked our questions online over Teams}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\wss{There are also columns for lines added and lines deleted to give a sense of
the magnitude of each team member's contributions.  Note that these numbers can
be somewhat misleading, as a team member who does refactoring may have high
numbers in both columns, while a team member who implements a large new feature
may have a high number of lines added, but few lines deleted.  These numbers
will be interpreted with care.}

\begin{table}[H]
\centering
\begin{tabular}{lllll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent} & \textbf{Lines Added} &
\textbf{Lines Deleted}\\
\midrule
Total & 204 & 100\% & 26328 & 7228\\
Angela Zeng & 64 & 31\% & 7390 & 1367\\
Ann Shi & 53 & 26\% & 2055 & 1683\\
Manan Sharma & 50 & 25\% & 12805 & 575\\
Ibrahim Sahi & 32 & 16\% & 1027 & 709\\
Stanley Chen & 5 & 2\% & 0 & 0\\
\bottomrule
\end{tabular}
\end{table}

\wss{
    The number of commits made may not accurately depict the amount of work that has been done by each member. Work was done by Manan, Ann and Stanley on the realtime application of the project on a seperate unmerged branch of a seperate private repository (SocialEyes) made from our supervisors. 13 commits were made with a total of 208 additions and 56 deletions.
    Angela and Ibrahim worked on more of the research side of the project, gathering data and information of various computer vision libraries to help with the development of the project.
}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Angela Zeng & 41 & 15 \\
Ann Shi & 27 & 24 \\
Manan Sharma & 10 & 6 \\
Ibrahim Sahi & 2 & 1 \\
Stanley Chen & 8 & 6 \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{CICD via GitHub Actions}

\wss{Say how CICD technology is used and will be used in your project.}

\wss{Provide links to your CICD yaml files}

\section{Extras}

\wss{What is the plan (as documented in TeamComposition.csv) for the team's
extras?  Should the extras be modified now that the team knows more about the
project?}


\section{Team Charter Trigger Items}

\wss{Provide a summary of the quantified triggers identified in the team's
charter.}

\wss{Provide a list of any violations of the triggers.  If the team wishes, the
violations can be summarized on aggregate, instead of naming specific team
members.}

\wss{Provide a plan to address the violations.  This could include revising the
triggers, if they are found to be too weak, strong or ambiguous.} \\

The team established clear triggers to maintain accountability and progress. Members are expected to attend one tutorial meeting and one additional weekly meeting, with a 10-minute grace period for lateness. Missing meetings without prior notice or a valid excuse is considered a violation. Tasks are expected to be completed by agreed-upon deadlines, and consistently late or incomplete work triggers follow-up and workload redistribution. Repeated lack of participation, poor-quality work, or uncooperative behavior are also treated as trigger conditions that require team discussion and, if needed, escalation to course staff. \\

Here are some of the violations that were noted: 
\begin{itemize}
    \item Minor punctuality issues occurred occasionally, with some team members arriving late to meetings.
    \item A small number of tasks were submitted past their deadlines due to scheduling or workload constraints.
\end{itemize} \\

To address these issues, the team created a dedicated Discord channel to clearly communicate deadlines and emphasize timely submissions. For punctuality, we agreed that occasional violations of the 10-minute grace period are acceptable, provided they do not become a recurring pattern.

\section{Additional Productivity Metrics}

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.  If not, please explicitly state that there are no additional
metrics.}

\wss{Additional metrics can include things like code reviews done, pull requests
created, count of joining meetings late, count of number of times contributions
had to be corrected, number of internal deadlines missed, test cases written, etc.}

\wss{We are looking for data on these metrics, not just a list of additional
metrics the team is planning on tracking.  However, if all you have is a plan,
please share it here.}

\end{document}